\section{Discussion}
Knowing that Poisson distribution generates homogeneous values and Power law generates heterogeneous values, we can see how it affects to the infection spread. 

In figure \ref{fig:sir_plots} we can see how the Poisson-Poisson network is the one that get more hosts infected (and consequentially more hosts recovered), but it starts slower than other networks. This is logical, since it is the most homogeneous network, the disease spreads at first slow because the nodes infected doesn't reach a huge amount of nodes, until many nodes are infected. If we compare it with any network with a power law anywhere, we see that the others grow faster at start, but they also start to fade with a smaller amount of nodes infected. This is because in heterogeneous networks, once the nodes with many connections recover, then the disease loses most of the infecting probability. Also in heterogeneous networks, there are more nodes with few connections that are harder to infect, which results in more nodes that never get infected. Then the networks with constant $P_l$ are the ones with the highest total infected hosts and also some of the fastest ones to spread. Here we can see directly how the homogeneity of $P_k$ affects to the speed, because as we previously stated, in the power law plot we can see how the spread speed is maximum but the total infected is better when it is homogeneous. Finally, comparing how the distribution of $P_l$ affects, we can see that it happens almost the opposite to $P_k$, more homogeneous results in more speed, but this time it still increase the max amount of infected nodes.

In figure \ref{fig:sis_plots} we can see a similar behavior than before. Again, if $P_k$ is more homogeneous, the number of infected nodes grows slower but more, and if $P_l$ is more homogeneous, it grows faster and more. With the SIS model we can see more clearly the rate of infection against the rate of recovery by looking the height where there seems to be a horizontal asymptote. If it is higher, then the recover rate is lower or the infection rate is higher. This asymptote seems to be related to the previous max amount of infected, since it is increased by homogeneous $P_k$ and $P_l$.